Multiphyscis modeling for the Fluoride-salt-cooled High-temperature Reactor (FHR)

### 2018-07-23 paper/main.tex
Updates from ShareLaTeX

As discussed before, the multiscale treatment is important in capturing the correct feedback behaviour, so the results shown hereafter are with the treatment.  
Figure \ref{fig:RI_pcm} shows the power and temperature evolution during a 1\$ or 0.5\$ reactivity insertion. 
 During the 1\$ prompt insertion transient, the core maximum fuel temperature is 1500$^{\circ}C$, below the safety limit(1600$^{\circ}C$). 
Coolant temperature is raised by only 100$^{\circ}C$ at the peak.

\begin{figure}[h]
    \centering
        \includegraphics[width=1\linewidth]{./images/diffusion/tmsr/RI/diff_pcm/power.png}
        \includegraphics[width=1\textwidth]{./images/diffusion/tmsr/RI/diff_pcm/T_flibe_max.png}
        \includegraphics[width=1\textwidth]{./images/diffusion/tmsr/RI/diff_pcm/T_fuel_max.png}
    \caption{RI transients results}
    \label{fig:RI_pcm}
\end{figure}

Figure \ref{fig:RI_time} shows the effect of the timescale of the reactivity insertion on the safety parameters. Without SCRAM, the reactor reaches the same end state due to reactivity feedback mechanisms. However, safety measures can take in place to mitigate the consequence if the transient is slow.

\begin{figure}[h]
    \centering
        \includegraphics[width=\textwidth]{./images/diffusion/tmsr/RI/diff_time/power.png}
        \includegraphics[width=\textwidth]{./images/diffusion/tmsr/RI/diff_time/T_flibe_max.png}
        \includegraphics[width=\textwidth]{./images/diffusion/tmsr/RI/diff_time/T_fuel_max.png}
    \caption{RI transients results}
    \label{fig:RI_time}
\end{figure}

%-------------------------------------------------------------------------------------------------------------------------
\subsection{Overcooling transients}

>>>>

% As discussed before, the multiscale treatment is important in capturing the correct feedback behaviour, so the results shown hereafter are with the treatment.  
% Figure \ref{fig:RI_pcm} shows the power and temperature evolution during a 1\$ or 0.5\$ reactivity insertion. 
%  During the 1\$ prompt insertion transient, the core maximum fuel temperature is 1500$^{\circ}C$, below the safety limit(1600$^{\circ}C$). 
% Coolant temperature is raised by only 100$^{\circ}C$ at the peak.

% \begin{figure}[h]
%     \centering
%         \includegraphics[width=1\linewidth]{./images/diffusion/tmsr/RI/diff_pcm/power.png}
%         \includegraphics[width=1\textwidth]{./images/diffusion/tmsr/RI/diff_pcm/T_flibe_max.png}
%         \includegraphics[width=1\textwidth]{./images/diffusion/tmsr/RI/diff_pcm/T_fuel_max.png}
%     \caption{RI transients results}
%     \label{fig:RI_pcm}
% \end{figure}

% Figure \ref{fig:RI_time} shows the effect of the timescale of the reactivity insertion on the safety parameters. Without SCRAM, the reactor reaches the same end state due to reactivity feedback mechanisms. However, safety measures can take in place to mitigate the consequence if the transient is slow.

% \begin{figure}[h]
%     \centering
%         \includegraphics[width=\textwidth]{./images/diffusion/tmsr/RI/diff_time/power.png}
%         \includegraphics[width=\textwidth]{./images/diffusion/tmsr/RI/diff_time/T_flibe_max.png}
%         \includegraphics[width=\textwidth]{./images/diffusion/tmsr/RI/diff_time/T_fuel_max.png}
%     \caption{RI transients results}
%     \label{fig:RI_time}
% \end{figure}

%-------------------------------------------------------------------------------------------------------------------------
\newpage
\subsection{Overcooling transients}
